rang: Reconstructing reproducible R computational environments with ease

### 2023-02-28 paper/paper.qmd
Update the abstract about Bioconductor

---
title: 'rang: Reconstructing reproducible R computational environments with ease'
tags:
  - R
  - reproducibility
  - docker
authors:
  - name: "Chung-hong Chan"
    orcid: 0000-0002-6232-7530
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften
  - name: "David Schoch"
    orcid: 0000-0003-2952-4812
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften    
abstract: |
  A complete description of the computational environment is often missing when researchers share their materials. Without such description, software obsolescence and missing system components can jeopardize computational reproducibility in the future, even when data and computer code are available. The R package rang is a complete solution for generating instructions for other researchers to completely reconstruct the computational environment at a specific time point. The reconstruction process, based on Docker, has been tested for R code as old as 2005 and does not depend on the long term availability of any commericial service. The description generated by rang satisfies the definition of a reproducible research compendium and can be shared as such.
keywords:
  - R
  - reproducibility
  - docker
year: 2023
bibliography: paper.bib
format:
  pdf: default
  arxiv-pdf:
    keep-tex: true    
---

# Statement of need

@@

@@

`resolve()` queries various web services from the r-hub project of the R Consortium for information about R packages at a specific time point that is necessary for reconstructing a computational environment, e.g. recursive dependencies, system requirements, and R version. For instance, if there was a computational environment constructed on 2020-01-16 (called "snapshot date") with the several natural language processing R packages, `resolve()` can be used to resolve all the dependencies of these R packages. Currently, `rang` supports both CRAN and GitHub packages.

@@

For the sake of completeness, the instructions for building and running the Docker container for Unix-like systems are included here.

@@

>>>>

---
title: 'rang: Reconstructing reproducible R computational environments with ease'
tags:
  - R
  - reproducibility
  - docker
authors:
  - name: "Chung-hong Chan"
    orcid: 0000-0002-6232-7530
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften
  - name: "David Schoch"
    orcid: 0000-0003-2952-4812
    affiliation: GESIS Leibniz-Institut für Sozialwissenschaften    
abstract: |
  A complete declarative description of the computational environment is often missing when researchers share their materials. Without such description, software obsolescence and missing system components can jeopardize computational reproducibility in the future, even when data and computer code are available. The R package rang is a complete solution for generating the declarative description for other researchers to automatically reconstruct the computational environment at a specific time point. The reconstruction process, based on Docker, has been tested for R code as old as 2005 and does not depend on the long term availability of any commercial service. The description generated by rang satisfies the definition of a reproducible research compendium and can be shared as such. In this contribution, we show how rang can be used to make otherwise unexecutable code, spanning from fields such as computational social science and bioinformatics, executable again. We also provide instructions on how to use rang to construct reproducible and shareable research compendium of current research.
keywords:
  - R
  - reproducibility
  - docker
year: 2023
bibliography: paper.bib
format:
  pdf: default
  arxiv-pdf:
    keep-tex: true    
---

# Introduction

@@

## Existing solutions

@@

`resolve()` queries various web services from the r-hub project of the R Consortium for information about R packages at a specific time point that is necessary for reconstructing a computational environment, e.g. recursive dependencies, system requirements, and R version. For instance, if there was a computational environment constructed on 2020-01-16 (called "snapshot date") with the several natural language processing R packages, `resolve()` can be used to resolve all the dependencies of these R packages. Currently, `rang` supports CRAN, Bioconductor, and GitHub packages.

@@

For the sake of completeness, the instructions for building and running the Docker container on Unix-like systems are included here.

@@

## Recover a removed Bioconductor package

# Generating a research compendium

# Conclusion
